### 2014-04-24 path_volume_choice.tex
updated path contraction text and image segmentation

An alternative approach to estimating the prostate volume was to reconstruct
the prostate capsule from serial whole mount histology slides of the prostate.
This approach, however, was not chosen because the formalin fixation process
can cause up to $\sim$30\% contraction of the tissue [BUCK CITATION], the
$\sim$3 mm slice thickness introduces error, and tearing / folding of tissue on
the whole mount slides introduce additional artifacts that need to be
compensated for in the volume estimation process.  Finally, differences in the
tissue orientation on each whole mount slide would require an image
registration process to align all of the slides, introducing another source of
error in the process.

>>>>

An alternative approach to estimating the prostate volume was to reconstruct
the prostate capsule from serial whole mount histology slides of the prostate.
This approach, however, was not chosen because the formalin fixation process
can cause 0-25\% contraction of the tissue, the $\sim$3 mm slice thickness
introduces error, and tearing / folding of tissue on the whole mount slides
introduce additional artifacts that need to be compensated for in the volume
estimation process.  Finally, differences in the tissue orientation on each
whole mount slide would require an image registration process to align all of
the slides, introducing another source of error in the process.
